Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-02-28 paper/main.tex
section 3.1 completed

The previous lemma and its proof suggest implies that it is sufficient to

>>>>

The lemma suggests the following simplification of the whole formula
$\Phi_{C,K}$ built with $\mcycle_1(\vec{e})$. Before we build the
formula, we compute the equivalence $\sim$ on automata transitions and
remove all transitions except one of each class. Then we build the
formula for this pruned automaton as described above. The more
transitions we removed, the shorter formula with less $e_t$ variables
we obtain. If the formula $\Phi_{C,K}$ for the pruned automaton is
satisfiable and we derive $\rem$ and $\psi$ from its model, we can use
safely them also on the original automaton. We only need to extend
$\rem$ to all transitions such that it changes the acceptance marks on
all equivalent transitions in the same way.
